---
title: "An Analysis of Boston Neighborhoods"
author: "William Dean"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidytext)
library(dplyr)
library(ggmap)
library(topicmodels)
source("Figures.R")
```

# Overview

## Motivation

I really enjoy to travel especially visiting new cities around the world. I currently live in Boston, MA and have become very familiar with the area.

In a few of my most recent travels, I have found difficulty exploring bigger cities. When spending a few days in a certain city, I often end up spending a lot of time traveling within the city, not having enough time to connect with the people and the cultures.

## Goal

The *goal of this project* is to use data from areas and neighborhoods of cities to see how communities compare to others within the same city and also to others in different. 

When looking each neighborhood, there a few things that I am interested in measuring:

- What are the people like? How are the people that live in the area and what do people who visit think of the area and their time there.

- What are the living situations like? What kind of houses are in the area.

- What is the culture like? What are these communities known for and what are people talking about?

## Data

I wanted data that would reflect all these measure. Here are a few sources I found.

### Airbnb

The [Airbnb Datasets](http://insideairbnb.com/get-the-data.html) provides insight into many cities in the US and around the world. Not only are there reviews written by people who use the service, but also the listings have information about the neighborhood, the house, and the host.

Using this information will provide information for the people who live in the neighborhood, details of the neighborhoods from the hosts, and the experiences of the people who visit.

### Twitter

Twitter data gives insight to what is going on within a neighborhood, and what people are talking about. This accomplished trying to capture the neighborhood culture and potentially what people are like.

### Selected Data

I ended looking at the Boston data mainly and also using data from Chicago. There were a few limitations with the Airbnb data from chicago where only the house listing was provided. With it, there was no information about the host, or the reviews themselves from the people who stayed there. 

# Boston

## People from each Neighborhood

### Hosts

Looking at the host information wrote about themselves 

```{r, echo = FALSE, message = FALSE, warning = FALSE}
load("BHost.tfidf.Rda")
load("BHost.2.Rda")
BHost.lda <- BHost.2 %>% 
    cast_dtm(neighbourhood, text, n) %>% 
    LDA(k = 10) %>% 
    tidy(matrix = "gamma") %>% 
    group_by(document) %>% 
    top_n(1, gamma)
ggplot(left_join(BHost.lda,boston.map, by = c("document" = "Name"))) + 
    geom_polygon(aes(Long, Lat, fill = factor(topic), group = document), color = "black") + theme_nothing()
```

### People's Reviews

```{r, echo = FALSE, message = FALSE, warning = FALSE}
load("BReview.2.Rda")
BReview.lda <- BHost.2 %>% 
    cast_dtm(neighbourhood, text, n) %>% 
    LDA(k = 10) %>% 
    tidy(matrix = "gamma") %>% 
    group_by(document) %>% 
    top_n(1, gamma)
ggplot(left_join(BReview.lda,boston.map, by = c("document" = "Name"))) + 
    geom_polygon(aes(Long, Lat, fill = factor(topic), group = document), color = "black") + theme_nothing()
```

## Boston Neighborhoods


### Neighborhood Descriptions

```{r, echo = FALSE, message = FALSE, warning = FALSE}
load("BNeigh.2.Rda")
BNeigh.lda <- BNeigh.2 %>% 
    cast_dtm(neighbourhood, text, n) %>% 
    LDA(k = 10) %>% 
    tidy(matrix = "gamma") %>% 
    group_by(document) %>% 
    top_n(1, gamma)
ggplot(left_join(BNeigh.lda,boston.map, by = c("document" = "Name"))) + 
    geom_polygon(aes(Long, Lat, fill = factor(topic), group = document), color = "black") + theme_nothing()
```

### Housing

```{r, echo = FALSE, message = FALSE, warning = FALSE}
load("BHouse.2.Rda")
BHouse.lda <- BHouse.2 %>% 
    cast_dtm(neighbourhood, text, n) %>% 
    LDA(k = 10) %>% 
    tidy(matrix = "gamma") %>% 
    group_by(document) %>% 
    top_n(1, gamma)
ggplot(left_join(BHouse.lda,boston.map, by = c("document" = "Name"))) + 
    geom_polygon(aes(Long, Lat, fill = factor(topic), group = document), color = "black") + theme_nothing(tit)
```

# Comparison of Boston and Chicago

# Conclusion



